Continuous voting by approval and participation

### 2015-04-24 ApresentacoesArtigos/collectiveRanking/paper.tex
refinada revisao

\title{Continuous voting by approval and participation indexes} % For titles, only capitalize the first letter

@@

\begin{abstract}
In finding the adequate way to prioritize proposals, the Brazilian participation community agreed about an approval index and a participation index.
Both practice and literature is constantly handled by the experts involved, and the formalization of such model and indexes seems novel.
Also, the relevance of this report is strengthened by the nearby use of these indexes by the Brazilian General Secretariat of the Republic to raise and prioritize proposals about public health care in open processes.
\end{abstract}

@@

\section{}
%------------------------------------------------
% aqui já mando toda intro com as infos que cavei ontem.
Online decision making is a kind of recommendation system with special appeal for online social participation and electronic governments. This poses challenges on the design of such
processes regarding validity, security and the adequate indicators. Indeed,
the processes themselves vary, and the fact that the ranking indexes presented here seem not to be
formalized and published is an evidence that such online decision making is very recent phenomena.

The main contribution of this report is the indexes for
an online voting process~\cite{issue1,issue2,tabRonald} with the following characteristics:
\begin{itemize}
    \item proposals might be inserted by voters after the voting phase started.
    \item Voting might be extended as a permanent process. In other words, voting on and adding new proposals might be open continuously.
    \item A proposal is presented to a voter one by one as random outcomes of all proposals.
    \item Each vote might be of one and only type among: ``approve'', ``disapprove'' and ``indifferent''.
    \item Voters vote without authentication.
    \item Intended mostly for national rankings, but can also be local or have foreign participation.
    \item Should result in a ranking of proposals to assist public management.
\end{itemize}

@@

\section{Discussion}
These are the best estimates the researchers designed,
suitable for current needs and not found (yet) in literature.
The following questions should be answered in near future:
\begin{itemize}
	\item Are there more adequate measures for ranking proposals in the given setting?
    \item What are strong and weak aspects of the approach for collective recommendation?
    \item What thresholds will be the choice of community and will they be adjusted in time?
    \item Are there really no previous formalized solution to this problem in the exact setting? If there is, what comparisons can we make on design and outcomes?
    \item To which extent will participation community and public managers legitimize this approach?
\end{itemize}

>>>>

\title{Continuous voting by approval and participation} % For titles, only capitalize the first letter

@@

\begin{abstract}
In finding the adequate way to prioritize proposals, the Brazilian participation community agreed about two indexes of approval and of participation.
Both practice and literature is constantly handled by the experts involved, and the formalization of such model and metrics seems novel.
Also, the relevance of this report is strengthened by the nearby use of these indexes by the Brazilian General Secretariat of the Republic to raise and prioritize proposals about public health care in open processes.
\end{abstract}

@@

\section{}
%------------------------------------------------
% aqui já mando toda intro com as infos que cavei ontem.
Online decision making is a kind of recommendation system with special appeal for online social participation and electronic governments. This poses challenges on the design of such
processes regarding validity, security and the adequate indicators. Indeed,
the processes themselves vary, and the fact that the indexes presented here seem not to be
formalized and published is an evidence that such online decision making is very recent phenomena.

The main contribution of this report is a modeling for
an online voting process~\cite{issue1,issue2,tabRonald} with the following characteristics:
\begin{itemize}
    \item proposals might be inserted by voters after the voting phase started.
    \item Voting might be extended as a permanent process. In other words, voting on and adding new proposals might be open continuously.
    \item A proposal is presented to a voter one by one as random outcomes of all proposals.
    \item Each vote might be of one and only type among: ``approve'', ``disapprove'' and ``indifferent''.
    \item Voters vote without authentication.
    \item Intended mostly for national rankings, but can also be local or have foreign participation.
    \item Should result in a ranking of proposals to assist public management.
\end{itemize}

@@

\section{Discussion}
The above estimates are the best fit the researchers could deliver,
suitable for current needs and not found (yet) in literature.
The following questions should be answered in near future:
\begin{itemize}
	\item Are there more adequate metrics for ranking proposals in the given setting?
    \item What are strong and weak aspects of the approach for collective recommendation?
    \item What thresholds will be the choice of community and will they be adjusted in time?
    \item Are there really no previous formalized model of this setting? If there is, what comparisons can we make on design, metrics and outcomes?
    \item To which extent will participation community and public managers legitimize this approach?
	\item What is the impact of this technological approach in public health care, social participation and the scientific community?
\end{itemize}
